---
title: "LysoDC project - Octonary analysis - Analysis with Monocle"
output:
  html_document: 
    theme: cerulean
    toc: true
    toc_float: false
    toc_depth: 4
  pdf_document: default
---

[//]: # "Global documentation on Monocle can be found on:" 
[//]: # "http://cole-trapnell-lab.github.io/monocle-release/docs/"


```{r setOptions, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE, fig.keep="all")
```

[//]: # "Load the libraries"
```{r loadLibraries, echo=FALSE, warning=FALSE, message=FALSE}
library( knitr)
library( monocle)
library( ggplot2)
library( reshape2)
library( magrittr)
library( plyr)
library( dplyr)
library( DT)
library( grid)
library( pagoda2)
library( d3heatmap)
```

[//]: # "Define some constants"
```{r defineConstants, echo=FALSE, warning=FALSE, message=FALSE}
WORKING_DIR=Sys.getenv( "WORKING_DIR")

SCRIPT_DIR = file.path( WORKING_DIR, "src/step8")
DATA_DIR = file.path( WORKING_DIR, "data/step8")
INPUT_DIR = file.path( DATA_DIR, "input")
OUTPUT_DIR = file.path( DATA_DIR, "output")
dir.create( OUTPUT_DIR, showWarnings = FALSE)
```

[//]: # "Load the various chunks in the various files"
```{r readChunks, echo=FALSE, warning=FALSE, message=FALSE}
read_chunk( path=file.path( SCRIPT_DIR, "prepare_data.R"))
read_chunk( path=file.path( SCRIPT_DIR, "analysis_classify_cells.R"))
read_chunk( path=file.path( SCRIPT_DIR, "analysis_pseudotime.R"))
```

## Single-cell Analysis with Monocle

### Loading and building data
In this section, we load the data, normalize them using the Monocle size factor method, identify genes expressed by a minimum of cells and look at the expression of those genes. 
```{r loadingData, fig.keep="all", results='asis', echo=FALSE, warning=FALSE, message=FALSE}
<<load_data>>
<<build_data>>
<<filter_data>>
```  

### Classifying cells by type using markers
Monocle provides a simple system for tagging cells based on the expression of marker genes of your choosing. You simply provide a set of functions that Monocle can use to annotate each cell. For example, you could provide a function for each of several cell types. These functions accept as input the expression data for each cell, and return TRUE to tell Monocle that a cell meets the criteria defined by the function. So you could have one function that returns TRUE for cells that express myoblast-specific genes, another function for fibroblast-specific genes, etc. 

```{r classifyCellsByType, fig.keep="all", results='asis', echo=FALSE, warning=FALSE, message=FALSE}
<<classify_cells_by_type>>
```  

### Clustering cells with with markers
First, we'll select a different set of genes to use for clustering the cells. Before we just picked genes that were highly expressed and highly variable. Now, we'll pick genes that co-vary with our markers. In a sense, we'll be building a large list of genes to use as markers.

```{r classifyCellsWithMarkers, fig.keep="all", results='asis', echo=FALSE, warning=FALSE, message=FALSE}
<<classify_cells_with_markers>>
```  

### Pseudo time analysis

Here we will apply the pseudo-time analysis from Monocle using the data from the "with markers" analysis and the 100 best markers.

```{r choosePseudotimeContext, echo=TRUE, warning=FALSE, message=FALSE}
filtered_cds_for_pseudotime = filtered_cds_cell_type
signature_genes_for_pseudotime =  unique( selectTopMarkers( marker_spec, 100)$gene_id)
```  

```{r pseudotimeAnalysis, fig.keep="all", results='asis', echo=FALSE, warning=FALSE, message=FALSE}
<<pseudotime_analysis>>
```  