---
title: "LysoDC project - Septenary analysis - Refinement of Velocity analysis"
output:
  html_document: 
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 4
  pdf_document: default
---

[//]: # "Global documentation on Velocyto can be found on:" 
[//]: # "http://velocyto.org/"
[//]: # "For R Analysis of Velocyto results : http://pklab.med.harvard.edu/velocyto/notebooks/R/DG1.nb.html"
[//]: # R -e "library( knitr);rmarkdown::render('JPGlab_LysoDC_SeptenaryAnalysis.Rmd')"


```{r setOptions, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

[//]: # "Load the libraries"
```{r loadLibraries, echo=FALSE, warning=FALSE, message=FALSE}
library( knitr)
library( ggplot2)
library( reshape2)
library( magrittr)
library( plyr)
library( dplyr)
library( DT)

library( velocyto.R)
library( igraph)
library( pagoda2)
library( Seurat)
library( cluster)

WORKING_DIR=Sys.getenv( "WORKING_DIR")

SCRIPT_DIR = file.path( WORKING_DIR, "src/step7")
DATA_DIR = file.path( WORKING_DIR, "data/step7")
INPUT_DIR = file.path( DATA_DIR, "input")
OUTPUT_DIR = file.path( DATA_DIR, "output")
VELOCYTO_INPUT_DIR = INPUT_DIR

dir.create( OUTPUT_DIR, showWarnings = FALSE)
```

[//]: # "Load the various chunks in the various files"
```{r readChunks, echo=FALSE, warning=FALSE, message=FALSE}
read_chunk( path=file.path( SCRIPT_DIR, "prepare_reload_data.R"))
read_chunk( path=file.path( SCRIPT_DIR, "analysis_improve_rnavelocity_plot.R"))
```

```{r loadAllFunctions, echo=FALSE, warning=FALSE, message=FALSE}
<<load_all_functions>>
```

# Loading data from previous analysis

In this section, we load the R objects produced by the Senary analysis (step6)
in order to get exactly the same data for further analysis and plotting.
```{r reloadData, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
<<reload_data>>
```

# Refinement of analysis done with Velocyto

## Improve RNA velocity resulting plots

In this section we simply apply new parameters for RNA velocity resulting plots in order to have
a better visual result.
```{r improveRnavelocityPlot, echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
<<improve_rnavelocity_plot>>
```

## Analyze bassins of emission and attractions

In this section we try to identifu the cells that are in bassins of emission
(cells that are progenitor) and cells that are in bassins of attraction (cells
that are in terminal differentiation state).

```{r analyzeVelocityBassins,
echo=FALSE, warning=FALSE, message=FALSE, results="asis"}
<<analyze_velocity_bassins>>
```

