---
title: "LysoDC project"
output:
  html_document: 
    theme: cerulean
    toc: true
    toc_float: true
    toc_depth: 4
---

```{r setOptions, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error = TRUE)
```

[//]: # "Load the libraries"
```{r loadLibraries, echo=FALSE, warning=FALSE, message=FALSE}
library( knitr)
library( Seurat)
library( magrittr)
library( plyr)
library( dplyr)
library( DT)
library( grid)

SCRIPT_DIR = file.path( WORKING_DIR, "src/step1")
DATA_DIR = file.path( WORKING_DIR, "data/step1")
RAW_DATA_DIR = file.path( WORKING_DIR, "data/raw")
OUTPUT_DIR = file.path( DATA_DIR, "output")
dir.create( OUTPUT_DIR, showWarnings = FALSE)
VAR_GENES_MAX_NUMBER = 100

# TN,TP,DP,SP signature genes
SIGNATURE_GENES = c(
  "Cd24a", "Plet1", "Qpct", "Chn2", "H2-Ob", "Kmo", "AA467197", "Stap1", "Klrk1", "Klrb1b", 
  "Gpr141", "Cytip", "F11r", "Cd72", "Ccl22", "Ifitm1","Pvrl1", "Cbfa2t3", "Trem1", "Stat4", 
  "Pxdc1", "Lrrk2", "Adam8", "Il1b", "H2-Eb2", "Pcdh1", "Siglece", "Il1r2", "Emb", "Cd244",
  "Lpcat4", "Nedd4", "Clec4a4", "Adgre5", "Amica1", "Btg2", "Pianp", "Ece1", "Sucnr1", "Nup210",
  "Slc2a3", "Lmtk2", "Ciita", "Nav1", "H2-Ab1", "H2-DMb2", "Adam23", "Plxdc1", "Cd74",
  "H2-Eb1", "H2-Aa"
)

# Genes related to proliferation
GENE_LIST_PROLIFERATION = c( "Ccnb1", "Ccnb2", "Ccna2", "Cdc20", "Plk1", "Ube2c", "Cenpf", "Cenpa", "Aurka", "Mki67")

# Genes expressed by puttative contaminating cells
CONTAMINATION_GENES = c("Cd19", "Mzb1")

MONITORED_GENES = c( CONTAMINATION_GENES, GENE_LIST_PROLIFERATION, SIGNATURE_GENES)
```

[//]: # "Load the various chunks in the various files"
```{r readChunks, echo=FALSE, warning=FALSE, message=FALSE}
read_chunk( path=file.path( SCRIPT_DIR, "all_functions.R"))
read_chunk( path=file.path( SCRIPT_DIR, "prepare_data.R"))
read_chunk( path=file.path( SCRIPT_DIR, "analysis_variable_genes.R"))
read_chunk( path=file.path( SCRIPT_DIR, "analysis_cell_heterogeneity.R"))
```

[//]: # "Load all the required functions"
```{r loadFunctions, echo=FALSE, message=FALSE}
<<load_functions>>
```  

## Primary analysis on SC data

### Load of data
```{r loadingData, results='asis', echo=FALSE}
<<load_data>>
```  

### Quality Controls, filtering and normalization
```{r filteringData, results='asis', echo=FALSE}
<<filtering_data>>
<<normalizing_data>>
```

### Variables gene analysis

```{r findingVariableGenes, results='asis', echo=FALSE}
sc10x=NORMALIZED_FILTERED_SC10X
<<find_variable_genes_seurat_method>>
```

### Cell heterogeneity analysis

```{r heterogeneityAnalysisAllPopulations, results='asis', echo=FALSE}
<<heterogeneity_analysis_by_pca>>
```

### Elimination of sub-populations

In this analysis we will write to file not wanted cells in order to have
them removed from future analyses.

Cells in cluster 4 were analyzed as proliferative cells.

Cells in cluster 5 were analyzed as contiminating cells.

```{r removingMinoritySubPopulation, results='asis', echo=FALSE}

# Identify the cells to remove because they are proliferative cells
cell_to_remove_proliferation = colnames(sc10x@data)[ sc10x@ident == 4]
cat("<BR>Number of cells considered as proliferative:", length( cell_to_remove_proliferation))
cat("<BR>Their identities will be stored in file 'excluded_cells_proliferation.txt'.")
write.table( data.frame( cellid = cell_to_remove_proliferation), file=file.path( OUTPUT_DIR, "excluded_cells_proliferation.txt"), quote = FALSE, col.names = TRUE, row.names = FALSE, sep="\t")

# Identify the cells to remove because they are contamination cells
cell_to_remove_contamination = colnames( sc10x@data)[ sc10x@ident == 5]
cat("<BR>Number of cells considered as contamination:", length( cell_to_remove_contamination))
cat("<BR>Their identities will be stored in file 'excluded_cells_contamination.txt'.")
write.table( data.frame( cellid = cell_to_remove_contamination), file=file.path( OUTPUT_DIR, "excluded_cells_contamination.txt"), quote = FALSE, col.names = TRUE, row.names = FALSE, sep="\t")

# Identify the cells to keep and export the filtered raw expression table to file
cell_to_keep = colnames( sc10x@data)[ sc10x@ident %in% c(0,1,2,3)]
cat("<BR>Number of cells to keep:", length( cell_to_keep))

# Export raw expression matrix with only kept cells to file
df_raw_to_export = as.data.frame( as.matrix( sc10x@raw.data))[ , cell_to_keep]
cat("<BR>Raw expression matrix with only kept cells will be stored in file 'filtered_raw_expression_matrix.csv'")
write.table( df_raw_to_export, file = file.path( OUTPUT_DIR, "filtered_raw_expression_matrix.csv"), quote = FALSE, col.names = TRUE, row.names = TRUE, sep="\t")

# Export normalized expression matrix with only kept cells to file
df_norm_to_export = as.data.frame( as.matrix( sc10x@data))[ , cell_to_keep]
cat("<BR>Normalized expression matrix with only kept cells will be stored in file 'filtered_normalized_expression_matrix.csv'")
write.table( df_norm_to_export, file = file.path( OUTPUT_DIR, "filtered_normalized_expression_matrix.csv"), quote = FALSE, col.names = TRUE, row.names = TRUE, sep="\t")


```
